Convex Surrogates via Polyhedral Losses

### 2019-04-30 neurips-19/cvx-fin.tex
Jessie updating the reading list

	 \item To read in more detail: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
	 \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf}
\end{itemize}

>>>>

	 \item Ranking losses: \url{http://proceedings.mlr.press/v19/gao11a/gao11a.pdf}
	 Their Theorem 6 is slightly depressing: no consistent surrogate (by their def) for ranking.
	 Theorem 7: A New Hope. (For partial ranking)
	 Suggests that $\phi(x) = -x$ could be a valid convex function so that $\Phi(\textbf{f}(X), Y) = \sum_{y_i < y_j} a_Y (f_i(X) - f_j(X))$ is a consistent surrogate for partial ranking.

	 \item \url{http://web.stanford.edu/~jduchi/projects/DuchiMaJo10.pdf} introduces a graph-based notion of consistency.
	 Seems to mostly prove inconsistency of common losses.

	 \item \url{https://pubs.rsna.org/doi/pdf/10.1148/radiology.143.1.7063747} Section 3 on the Wilcoxan statistic might be of interest.  It gives the discrete score, but not a surrogate.  
	 $S(x,y) = 1$ if $x > y$, $1/2$ if $x=y$ and $0$ otherwise.\

	 \item \url{https://www.cc.gatech.edu/~zha/CS8803WST/ranking.pdf} Section 5.2.  Equation 8 might be of interest, or possibly modified to be useful for us.

	 \item \url{http://jmlr.csail.mit.edu/papers/volume5/zhang04b/zhang04b.pdf} Section 4 in general might be handy, asmight Appendix A.
	 \jessie{I think this one might be one of our best shots at an example.}

	 \item To read: \url{http://www.jmlr.org/papers/volume10/rudin09b/rudin09b.pdf}

\end{itemize}
